% Tento soubor nahraďte vlastním souborem s přílohami (nadpisy níže jsou pouze pro příklad)
% This file should be replaced with your file with an appendices (headings below are examples only)

% Umístění obsahu paměťového média do příloh je vhodné konzultovat s vedoucím
% Placing of table of contents of the memory media here should be consulted with a supervisor
%\chapter{Obsah přiloženého paměťového média}

\chapter{Installation details}
Chapter covers the~details of~running the~Restty application on~local computer. At~first it is required to~copy the~folder
with~the~project to~the~local disk. Then it is neccessary to~follow the~procedure that consists of~two parts. 
The~first part is used to~start up the~backend of~the~application and~the~steps needed to~run Restty's backend are as~follows:

\begin{enumerate}
  \item Download and~install the~Java Development Kit of~version 1.8.
  \item Download and~install the~Apache Maven project management tool in~version 3 or~later.
  \item Add the~Java and~Maven to~the~system variables if~running the~application on~Windows.
  \item In~the~root folder of~the~project run the~command -- \textit{mvn clean install} which installs
		neccessary dependencies required by~the~application.
  \item To~start the~application, in~the \textit{/backend} folder, run the~command -- \textit{mvn spring-boot:run}. 
\end{enumerate}

The~second part is to~start up the~frontend of~the~application which is needed for~Restty to~be fully functional.
To~start up the~frontend, following steps must be executed:

\begin{enumerate}
  \item Download latest version of~NodeJS.
  \item Install the~\textit{angular-cli} using the~command -- \textit{npm install -g @angular-cli}.
  \item To~start the~application, run the~\textit{ng serve --proxy-conf proxy.conf.json} command
  	 	in~the~\textit{/frontend/src/main/frontend} directory. 
\end{enumerate}